Heritability

### 2022-11-21 04-heritability.Rmd
move manuscript location

save(p_herit, file = 'Output/herit_plot.RData')

ggsave('Manuscript/fig2.jpg', p_herit, width = 4, height = 3) 
ggsave('Manuscript/fig2.svg', p_herit, width = 4, height = 3)

@@

```{r save_heritability}
save(herit_model, file = 'Output/herit_model.RData')
```

@@

save(p_herit_each, file = 'Output/herit_plot.RData')

>>>>

# save(p_herit, file = 'Output/herit_plot.RData')
# 
# ggsave('Manuscript/fig2.jpg', p_herit, width = 4, height = 3) 
# ggsave('Manuscript/fig2.svg', p_herit, width = 4, height = 3)

@@

```{r save_heritability}
# save(herit_model, file = 'Output/herit_model.RData')
```

@@

save(p_herit_each, file = 'Output/herit_plot.RData')
save(herit_model, file = 'Output/herit_model.RData')
